From heartbeat to data -- Using wearable fitness trackers as an affordable approach to assess teacher stress

### 2024-09-23 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
soweit final

>>>>

```{r plots_appendix, include=FALSE}
mods <-   
  df_regression %>% 
  split(.$time_span) %>% 
  map(~ lm(formula = heart_rate_std ~ 0 + ID + time:ID,
       data = .
       )
      )

graph_data <- 
  df_regression %>% 
  split(.$time_span)

example <- list(mod = mods$preparation, data = graph_data$preparation)

plot_list_appendix <- list(
  `Preparation Phase` = list(name = "Pre-Teaching Interval", mod = mods$preparation, data = graph_data$preparation),
  `Teaching Phase` = list(name = "Teaching Interval", mod = mods$teaching, data = graph_data$teaching),
  `Post Teaching Phase` = list(name = "Post-Teaching Interval", mod = mods$post, data = graph_data$post),
  `Interview Phase` = list(name = "Interview Interval", mod = mods$interview, data = graph_data$interview),
  `End Phase` = list(name = "End Interval", mod = mods$end, data = graph_data$end)
) %>% 
  map(~ ggplot(data = .$data,
               mapping = aes(x = time,  # Use the appropriate 'x' value (like 'work_hrs' in the original)
                             y = heart_rate_std,  # Use the appropriate 'y' value (like 'inc')
                             group = ID)) +
        geom_line(mapping = aes(y = fitted(.$mod)),  # Line for fitted values from the model
                  color = "blue",  # Adjust color for clarity
                  size = 1) +  # Line thickness
        geom_point(alpha = 0.5, size = 0.5) +  # Points with transparency and size
        facet_wrap(~ ID, nrow = 8) +  # Arrange plots by 'ID'
        xlab('Time (in Seconds)') +  # X-axis label (similar to 'Arbeitsstunden pro Woche')
        ylab('Heart Rate (Standardized)') +  # Y-axis label (similar to 'Nettoeinkommen')
        scale_x_continuous(breaks = c(0, 5, 10)) +  # Customize x-axis breaks as needed
        labs(title = .$name) +  # Title for each plot based on phase name
        theme_bw()  # Use a clean theme
      )

# 
# plot_list_appendix <- list(
#   `Preparation Phase` = list(name = "Pre-Teaching Interval", mod = mods$preparation, data = graph_data$preparation),
#      `Teaching Phase` = list(name = "Teaching Interval", mod = mods$teaching, data = graph_data$teaching),
#      `Post Teaching Phase` = list(name = "Post-Teaching Interval",mod = mods$post, data = graph_data$post),
#      `Interview Phase` = list(name = "Interview Interval",mod = mods$interview, data = graph_data$interview),
#      `End Phase` = list(name = "End Interval",mod = mods$end, data = graph_data$end)
#      ) %>% 
#   map(~ ggplot(data = .$data,
#                mapping = aes(x = time,
#                              y = heart_rate_std,
#                              group = ID)) +
#         geom_line(mapping = aes(y = fitted(.$mod)),
#                   color = "blue",
#                   size = 1) +
#         geom_point(alpha = 0.5,
#                    size = 0.5) +
#         scale_x_continuous(breaks = c(0, 5, 10)) +
#         labs(title = .$name,
#              y = "Heart Rate (Standardized)",
#              x = "Time (in Seconds)") +
#         facet_wrap( ~ ID, nrow = 8) +
#         theme_apa()
#       )

preparation_plot <- plot_list_appendix$`Preparation Phase`

teaching_plot <- plot_list_appendix$`Teaching Phase`

post_teaching_plot <- plot_list_appendix$`Post Teaching Phase`

interview_plot <- plot_list_appendix$`Interview Phase`

end_plot <- plot_list_appendix$`End Phase`

ggsave(preparation_plot,
       filename = "plots_publication/plot_preparation_appendix.pdf",
       width = 25,
       height = 30,
       units = "cm")

ggsave(teaching_plot,
       filename = "plots_publication/plot_teaching_appendix.pdf",
       width = 25,
       height = 30,
       units = "cm")

ggsave(post_teaching_plot,
       filename = "plots_publication/plot_post_teaching_appendix.pdf",
       width = 25,
       height = 30,
       units = "cm")

ggsave(interview_plot,
       filename = "plots_publication/plot_interview_appendix.pdf",
       width = 25,
       height = 30,
       units = "cm")

ggsave(end_plot,
       filename = "plots_publication/plot_end_appendix.pdf",
       width = 25,
       height = 30,
       units = "cm")

```{=latex}
\newpage
\appendix
\section*{Appendix}

\setcounter{figure}{0}  % Reset figure numbering

\renewcommand{\thefigure}{A\arabic{figure}}  % Figures labeled A1, A2, etc.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.7\textwidth]{appendix_figure1.png}
  \caption{Laboratory setting of the micro-teaching unit. Note. The setting included three actors as the class (left) and a teacher (participant, right).}
  \label{micro-teaching}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.7\textwidth]{appendix_figure2.png}
  \caption{Laboratory setting of the interview. Note. The experimenter and participant watched the previously taught micro-teaching unit on video.}
  \label{laboratory}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/plot_preparation_appendix.pdf}
  \caption{bla..}
  \label{preparation}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/plot_teaching_appendix.pdf}
  \caption{bla..}
  \label{teaching}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/plot_post_teaching_appendix.pdf}
  \caption{bla..}
  \label{post_teaching}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/plot_interview_appendix.pdf}
  \caption{bla..}
  \label{interview}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/plot_end_appendix.pdf}
  \caption{bla..}
  \label{end}
\end{figure}
```

### 2024-09-23 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex
soweit final

\begin{verbatim}
## Warning: Using `size` aesthetic for lines was deprecated in ggplot2 3.4.0.
## i Please use `linewidth` instead.
## This warning is displayed once every 8 hours.
## Call `lifecycle::last_lifecycle_warnings()` to see where this warning was
## generated.
\end{verbatim}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/plot_teaching_appendix.pdf}
  \caption{bla..}
  \label{preparation}
\end{figure}

>>>>

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/plot_teaching_appendix.pdf}
  \caption{bla..}
  \label{teaching}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/plot_post_teaching_appendix.pdf}
  \caption{bla..}
  \label{post_teaching}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/plot_interview_appendix.pdf}
  \caption{bla..}
  \label{interview}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/plot_end_appendix.pdf}
  \caption{bla..}
  \label{end}
\end{figure}
